Trans-Dimensional Inference for Gravitational Lens Substructures

### 2015-06-24 Papers/ms.tex
Define empirical measure

The {\it empirical measure} of the substructure positions is a function that
takes the substructure positions $()$

>>>>

The {\it empirical measure} of the substructure positions is a functional that
takes the substructure positions $(x_i^{\rm lens}, y_i^{\rm lens})$ and
produces a ``density function'' over two dimensions, composed of delta
functions at the positions themselves:

\begin{eqnarray}
\left\{
(x_i^{\rm lens}, y_i^{\rm lens})
\right\}_{i=1}^{N_{\rm lens}}
\Longrightarrow
\sum_{i=1}^{N_{\rm lens}}
\delta\left(x - x_i^{\rm lens}, y_i^{\rm lens}, y - y_i^{\rm lens}\right).
\end{eqnarray}
